Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-18 talk/pepm2011/paper.tex
customize line numbers in the code listing

\begin{figure}
\begin{lstlisting}[mathescape]
# arguments to the trace: $p_{0}$, $p_{1}$
guard_class($p_1$, BoxedInteger)
$i_2$ = get($p_1$, intval)
guard_class($p_0$, BoxedInteger)
$i_3$ = get($p_0$, intval)
$i_4$ = int_add($i_2$, $i_3$)
$i_9$ = int_add($i_4$, -100)

guard_class($p_0$, BoxedInteger)
$i_{12}$ = get($p_0$, intval)
$i_{14}$ = int_add($i_{12}$, -1)

>>>>

\begin{figure}
\begin{lstlisting}[mathescape,numbers=left,escapechar=|]
# arguments to the trace: $p_{0}$, $p_{1}$ |\setcounter{lstnumber}{2}|
guard_class($p_1$, BoxedInteger)
$i_2$ = get($p_1$, intval)
guard_class($p_0$, BoxedInteger)
$i_3$ = get($p_0$, intval)
$i_4$ = int_add($i_2$, $i_3$)
$i_9$ = int_add($i_4$, -100)
|\setcounter{lstnumber}{50}|
guard_class($p_0$, BoxedInteger) 
$i_{12}$ = get($p_0$, intval)
$i_{14}$ = int_add($i_{12}$, -1)
